### 2019-09-17 2019_neurips_vigil/appendix_model.tex
Updated model section. Cosmetic changes to other sections.
Table in appendix

\begin{figure}
	\includegraphics[width=\textwidth]{img/model2}
	\label{fig:model}
\end{figure}

@@

\begin{table}[t]
	\tiny

	\caption{COG test set accuracies for  SAMNet \& COG models. For the COG section, the results marked as 'paper' comes from the original COG paper ~\cite{yang2018dataset}, whereas the results marked as 'ours' come from our own experiments using the following implementation: https://github.com/google/cog }

	\resizebox{\textwidth}{!}{
		\centering
		\begin{tabular}{ccccccccccc}
			\toprule
			Model & & SAMNet & && && COG&& \\
			\cmidrule{2-5} \cmidrule{7-11} 
			&&&&& & paper & ours & ours & paper&\\
			\cmidrule{7-9} \cmidrule{10-11}
			Trained on       & canonical & canonical & canonical & hard &           &  canonical  & canonical  & canonical & hard \\ 
			Fine tuned on  & - & - & hard  & - &           & -   & - & hard & - \\ 
			Tested on        & canonical & hard & hard & hard &            &canonical  & hard & hard & hard  \\ 
			\midrule

			Overall accuracy & 98.0 & 91.6 & 96.5  & running &           & 97.6  & 65.9 & 78.1& 80.1 \\

@@

			AndCompareColor	&	93.5		&	82.7	&	89.2	&&		&81.9	&57.1& 60.7&	51.4
			\\ 
			AndCompareShape	&	93.2 		&	83.7	&	89.7	&&	&	80.0	&53.1	&50.3&50.7\\ 
			AndSimpleCompareColor	&	99.2	&		85.3	&	97.6	&	&	&99.7&	53.4&77.1&	78.2\\ 
			AndSimpleCompareShape	&	99.2&			85.8	&	97.6	&&	&	100.0	&56.7&79.3&	77.9\\ 
			CompareColor	&	98.1		&	89.3	&	95.9	&&		&99.2&	56.1&67.9&	50.1\\ 
			CompareShape	&	98.0	&		89.7	&	95.9	&&	&99.4	&66.8	&65.4&50.5
			\\ 
			Exist	&	100.0	&		99.7	&	99.8		&&	&	100.0&	63.5&96.1&	99.3\\ 
			ExistColor	&	100.0		&	99.6	&	99.9	&&	&	99.0&	70.9&99&	89.8\\ 
			ExistColorOf	&	99.9	&		95.5	&	99.7		& & &	99.7&	51.5&76.1&	73.1\\ 
			ExistColorSpace	&94.1		&	88.8	&	91.0	&& &	98.9	&72.8	&77.3&89.2\\ 
			ExistLastColorSameShape	&	99.5		&	99.4	&99.4	&&		&100.0	&65.0&62.5&	50.4
			\\ 
			ExistLastObjectSameObject	&	97.3	&		97.5	&	97.7	&&	&	98.0&	77.5	&61.7&60.2\\ 
			ExistLastShapeSameColor	&	98.2		&	98.5&	98.8	&&	&	100.0&	87.8&60.4&	50.3\\ 
			ExistShape	&	100.0	&	99.5	&	100.0	&&&	100.0&	77.1	&98.2&92.5\\ 
			ExistShapeOf	&	99.4		&	95.9	&	99.2	&&&100.0	&52.7&74.7&72.70\\ 
			ExistShapeSpace &	93.4		&	87.5	&	91.1	&&&97.7 &70	&89.8&89.80& \\
			ExistSpace	&	95.3	&	89.7	&	93.2	&&		&	98.9	&71.1	&88.1&92.8\\ 
			GetColor	&	100.0		&	95.8&	99.9	&& &	100.0&	71.4&83.1&	97.9\\ 
			GetColorSpace	&	98.0		&	90.0	&	95.0&	& &	98.2	&71.8&73.&	92.3\\ 
			GetShape	&	100.0		&	97.3&	99.9&	&	&	100.0  &83.5&89.2&	97.1
			\\ 
			GetShapeSpace	&	97.5	&	89.4	&	93.9	&&&	98.1  &78.7	&77.3&	90.3\\ 
			SimpleCompareShape	&	99.9		&	91.4	&	99.7	&	&&	100.0 & 67.7&96.7&	99.3\\ 
			SimpleCompareColor	&	100.0 		&	91.6  &	99.80&	&	&	100.0&	64.2&90.4&	99.3	  \\

			\bottomrule
		\end{tabular}
	}

>>>>

\begin{figure}
	\includegraphics[width=\textwidth]{img/model2}
	\label{fig:model2}
\end{figure}

@@

\begin{table}[t]
\caption{COG test set accuracies for SAMNet \& COG models. Below `paper' denotes results from~\cite{yang2018dataset} 
	while `code' denotes results of our experiments using their implementation~\cite{yang2018implement}}
\resizebox{\textwidth}{!}{
\centering
\begin{tabular}{ccccccccccc}
	\toprule
	Model & & SAMNet & && && COG&& \\
	\cmidrule{2-5} \cmidrule{7-11} 
	&&&&& & paper & ours & ours & paper&\\
	\cmidrule{7-9} \cmidrule{10-11}
	Trained on       & canonical & canonical & canonical & hard &           &  canonical  & canonical  & canonical & hard \\ 
	Fine tuned on  & - & - & hard  & - &           & -   & - & hard & - \\ 
	Tested on        & canonical & hard & hard & hard &            &canonical  & hard & hard & hard  \\ 
	\midrule

	Overall accuracy & 98.0 & 91.6 & 96.5  & 96.1 &           & 97.6  & 65.9 & 78.1& 80.1 \\

@@

	AndCompareColor			&	93.5	&	82.7	&	89.2	&	80.6	&	&	81.9	&	57.1	&	60.7	&	51.4	 \\
	AndCompareShape			&	93.2	&	83.7	&	89.7	&	80.1	&	&	80.0	&	53.1	&	50.3	&	50.7 \\
	AndSimpleCompareColor		&	99.2	&	85.3	&	97.6	&	99.4	&	&	99.7	&	53.4	&	77.1	&	78.2 \\
	AndSimpleCompareShape		&	99.2	&	85.8	&	97.6	&	99.2	&	&	100.0	&	56.7	&	79.3	&	77.9 \\
	CompareColor			&	98.1	&	89.3	&	95.9	&	99.7	&	&	99.2	&	56.1	&	67.9	&	50.1 \\
	CompareShape			&	98.0	&	89.7	&	95.9	&	99.2	&	&	99.4	&	66.8	&	65.4	&	50.5	 \\
	Exist				&	100.0	&	99.7	&	99.8	&	99.8	&	&	100.0	&	63.5	&	96.1	&	99.3 \\
	ExistColor			&	100.0	&	99.6	&	99.9	&	99.9	&	&	99.0	&	70.9	&	99	&	89.8 \\
	ExistColorOf			&	99.9	&	95.5	&	99.7	&	99.8	&	&	99.7	&	51.5	&	76.1	&	73.1 \\
	ExistColorSpace			&	94.1	&	88.8	&	91.0	&	90.8	&	&	98.9	&	72.8	&	77.3	&	89.2 \\
	ExistLastColorSameShape		&	99.5	&	99.4	&	99.4	&	98.0	&	&	100.0	&	65.0	&	62.5	&	50.4 \\
	ExistLastObjectSameObject	&	97.3	&	97.5	&	97.7	&	97.5	&	&	98.0	&	77.5	&	61.7	&	60.2 \\
	ExistLastShapeSameColor		&	98.2	&	98.5	&	98.8	&	97.5	&	&	100.0	&	87.8	&	60.4	&	50.3 \\
	ExistShape			&	100.0	&	99.5	&	100.0	&	100.0	&	&	100.0	&	77.1	&	98.2	&	92.5 \\
	ExistShapeOf			&	99.4	&	95.9	&	99.2	&	99.2	&	&	100.0	&	52.7	&	74.7	&	72.70 \\
	ExistShapeSpace			&	93.4	&	87.5	&	91.1	&	90.5	&	&	97.7	&	70	&	89.8	&	89.80 \\
	ExistSpace			&	95.3	&	89.7	&	93.2	&	93.3	&	&	98.9	&	71.1	&	88.1	&	92.8 \\
	GetColor			&	100.0	&	95.8	&	99.9	&	100.0	&	&	100.0	&	71.4	&	83.1	&	97.9 \\
	GetColorSpace			&	98.0	&	90.0	&	95.0	&	95.4	&	&	98.2	&	71.8	&	73.	&	92.3 \\
	GetShape			&	100.0	&	97.3	&	99.9	&	99.9	&	&	100.0	&	83.5	&	89.2	&	97.1	 \\
	GetShapeSpace			&	97.5	&	89.4	&	93.9	&	94.3	&	&	98.1	&	78.7	&	77.3	&	90.3 \\
	SimpleCompareShape		&	99.9	&	91.4	&	99.7	&	99.9	&	&	100.0	&	67.7	&	96.7	&	99.3 \\
	SimpleCompareColor		&	100.0	&	91.6	&	99.80	&	99.9	&	&	100.0	&	64.2	&	90.4	&	99.3 \\
	\bottomrule
\end{tabular}
}
